Meta-analysis

### 2020-05-22 04_MetaAnalysis.Rmd
Reword some of the examples after data has changed

   - The `recommended_plus` spray which has one or more follow-up sprays after first sign are likely to increase the mean grain yield.

   - `Late_plus` spray treatments showed the highest mean grain yield, and was significantly higher than the no spray control. However showed no difference to either of the `recommended` treatments.

@@

```{r variance_histograms}
hist_usq(slimmer_PM_dat$yield_error) # yield error is not normally distributed
hist_usq(log(slimmer_PM_dat$yield_error)) # a log transformation shows it is normally distributed 
```

@@

>>>>

   - The `Late_plus` spray which has one or more follow-up sprays after first sign are likely to increase the mean grain yield.

   - `Recommended_plus` spray treatments showed the highest mean grain yield, and was significantly higher than the no spray control. However showed no difference to either the `recommended` or `Late_plus` treatments.

@@

```{r variance_histograms}
hist_usq(slimmer_PM_dat$yield_error) # yield error is not normally distributed
hist_usq(log(slimmer_PM_dat$yield_error)) # a log transformation shows it is close to normally distributed 
```

@@

```{r Metafor-analysis}
PM_mv_AI <- rma.mv(
   yi,
   vi,
   mods = ~ slimmer_PM_dat$spray_management + slimmer_PM_dat$row_spacing + slimmer_PM_dat$host_genotype,
   method = "ML",
   random = list( ~ spray_management | trial_ref),
   struct = "UN",
   data = slimmer_PM_dat
)

summary(PM_mv_AI)
